---
title: "Workbench Transition Schedule"
---

Below you will find tables that indicate when a given lesson is expected to
transition to The Workbench along with a link to the preview and a GitHub issue
tracking progress on the conversion. 

::: {.callout-note}

## Note

The expected transition date is subject to change based on capacity of
the Carpentries Core Team.

:::

If you have any questions, please contact the curriculum team at 
curriculum at carpentries dot org

```{r setup, eval = FALSE, include = FALSE}
extract_tasklist <- function(issue) {
  title <- issue$title
  nr <- issue$number
  url <- issue$html_url
  f <- textConnection(issue$body)
  on.exit(close(f), add = TRUE)
  y <- tinkr::yarn$new(f)
  status <- as.logical(NA)
  complete <- 0
  total    <- 0
  tasks <- xml2::xml_find_all(y$body, ".//md:tasklist", ns = y$ns)
  if (length(tasks)) {
    status <- xml2::xml_attr(tasks, "completed") == "true"
    complete <- sum(status)
    total <- length(status)
    tasks <- xml2::xml_text(tasks)
  } else {
    tasks <- NA_character_
  }
  msg <- "{complete}/{total} tasks complete: (#{sprintf('%02d', nr)}) {title}"
  if (complete == total) {
    complete <- cli::style_bold(cli::col_blue(complete))
    cli::cli_alert_success(msg)
  } else {
    cli::cli_alert_info(msg)
  }

  tibble::tibble(lesson = title, issue = nr, task = tasks, complete = status, url = url)

}

get_tasks <- function(repo = "carpentries/lesson-transition", tags = "lesson") {
  issues <- gh::gh("GET /repos/{repo}/issues", per_page = 100, .limit = Inf,
    repo = repo, .params = list(labels = tags))
  purrr::map_dfr(issues, extract_tasklist)
}

makeit <- function(tab) {
  knitr::kable(tab[-1], 
    col.names = c("Expected Transition", "Lesson", "Preview", "Tracking Issue"), 
    align = "rllc") |> 
    clipr::write_clip()
}

library("dplyr")
library("purrr")
library("glue")
tasks <- get_tasks()

lessons <- tasks |>
 mutate(lesson = tolower(lesson)) |>
 arrange(lesson) |>
 select(lesson, issue) |>
 distinct() |>
 mutate(org = map_chr(strsplit(lesson, "/"), 1), 
   repo = map_chr(strsplit(lesson, "/"), 2))

summary <-  lessons |>
  mutate(preview = glue("[{repo} (:mag:)](https://fishtree-attempt.github.io/{repo}/)"), 
  tracking = glue("[#{issue}](https://github.com/carpentries/lesson-transition/issues/{issue})"), 
  lesson = glue("[{repo}](https://{org}.github.io/{repo}/)"), 
  date = as.Date("2023-05-01")) |>
  select(org, date, lesson, preview, tracking)

slist <- split(summary, summary$org)

```


## Carpentries

```{r}
#| label: cp-table
#| eval: false
#| echo: false
makeit(slist$carpentries)
```

| Expected Transition|Lesson                            |Preview                                   | Tracking Issue |
|---------:|:---------------------------------|:-----------------------------------------|:-------:|
|2023-04-04|[instructor-training](https://carpentries.github.io/instructor-training/)| (released :tada:) ||
|2023-04-20|[instructor-training-bonus-modules](https://carpentries.github.io/instructor-training-bonus-modules/)| (released :tada:) |[#32](https://github.com/carpentries/lesson-transition/issues/32)|

## Data Carpentry

::: {.callout-tip}

### Early transition lessons

Here is a link to tracking issues for lessons whose maintainers have elected to
transition before May: [early transition DataCarpentry
lessons](https://github.com/carpentries/lesson-transition/issues?q=is%3Aopen+is%3Aissue+label%3A%22early+transition%22++datacarpentry)

:::

```{r}
#| label: dc-table
#| eval: false
#| echo: false
makeit(slist$datacarpentry)
```

### Ecology

| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-05-01|[openrefine-ecology-lesson](https://datacarpentry.github.io/openrefine-ecology-lesson/)|[openrefine-ecology-lesson (:mag:)](https://fishtree-attempt.github.io/openrefine-ecology-lesson/)|[#53](https://github.com/carpentries/lesson-transition/issues/53)|
|2023-05-01|[python-ecology-lesson](https://datacarpentry.github.io/python-ecology-lesson/)|[python-ecology-lesson (:mag:)](https://fishtree-attempt.github.io/python-ecology-lesson/)|[#41](https://github.com/carpentries/lesson-transition/issues/41)|
|2023-04-04|[python-ecology-lesson-es](https://datacarpentry.github.io/python-ecology-lesson-es/)| (released :tada:) ||
|2023-05-01|[r-ecology-lesson](https://datacarpentry.github.io/r-ecology-lesson/)|[r-ecology-lesson (:mag:)](https://fishtree-attempt.github.io/r-ecology-lesson/)|[#55](https://github.com/carpentries/lesson-transition/issues/55)|
|2023-05-01|[spreadsheet-ecology-lesson](https://datacarpentry.github.io/spreadsheet-ecology-lesson/)|[spreadsheet-ecology-lesson (:mag:)](https://fishtree-attempt.github.io/spreadsheet-ecology-lesson/)|[#40](https://github.com/carpentries/lesson-transition/issues/40)|
|2023-04-21|[sql-ecology-lesson](https://datacarpentry.github.io/sql-ecology-lesson/)| (released :tada:) |[#57](https://github.com/carpentries/lesson-transition/issues/57)|

### Genomics

| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-04-28|[cloud-genomics](https://datacarpentry.github.io/cloud-genomics/)|[cloud-genomics (:mag:)](https://fishtree-attempt.github.io/cloud-genomics/)|[#50](https://github.com/carpentries/lesson-transition/issues/50)|
|2023-05-01|[genomics-r-intro](https://datacarpentry.github.io/genomics-r-intro/)|[genomics-r-intro (:mag:)](https://fishtree-attempt.github.io/genomics-r-intro/)|[#51](https://github.com/carpentries/lesson-transition/issues/51)|
|2023-05-01|[organization-genomics](https://datacarpentry.github.io/organization-genomics/)|[organization-genomics (:mag:)](https://fishtree-attempt.github.io/organization-genomics/)|[#54](https://github.com/carpentries/lesson-transition/issues/54)|
|2023-05-01|[shell-genomics](https://datacarpentry.github.io/shell-genomics/)|[shell-genomics (:mag:)](https://fishtree-attempt.github.io/shell-genomics/)|[#42](https://github.com/carpentries/lesson-transition/issues/42)|
|2023-05-01|[wrangling-genomics](https://datacarpentry.github.io/wrangling-genomics/)|[wrangling-genomics (:mag:)](https://fishtree-attempt.github.io/wrangling-genomics/)|[#58](https://github.com/carpentries/lesson-transition/issues/58)|

### Geospatial

| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-05-01|[organization-geospatial](https://datacarpentry.github.io/organization-geospatial/)|[organization-geospatial (:mag:)](https://fishtree-attempt.github.io/organization-geospatial/)|[#26](https://github.com/carpentries/lesson-transition/issues/26)|
|2023-05-01|[r-intro-geospatial](https://datacarpentry.github.io/r-intro-geospatial/)|[r-intro-geospatial (:mag:)](https://fishtree-attempt.github.io/r-intro-geospatial/)|[#25](https://github.com/carpentries/lesson-transition/issues/25)|
|2023-04-04|[r-raster-vector-geospatial](https://datacarpentry.github.io/r-raster-vector-geospatial/)| (released :tada:) ||

### Image Processing


| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-04-25|[image-processing](https://datacarpentry.github.io/image-processing/)| (released :tada:) |[#46](https://github.com/carpentries/lesson-transition/issues/46)|

### Socialsci


| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-04-28|[openrefine-socialsci](https://datacarpentry.github.io/openrefine-socialsci/)|[openrefine-socialsci (:mag:)](https://fishtree-attempt.github.io/openrefine-socialsci/)|[#49](https://github.com/carpentries/lesson-transition/issues/49)|
|2023-05-01|[python-socialsci](https://datacarpentry.github.io/python-socialsci/)|[python-socialsci (:mag:)](https://fishtree-attempt.github.io/python-socialsci/)|[#47](https://github.com/carpentries/lesson-transition/issues/47)|
|2023-04-04|[r-socialsci](https://datacarpentry.github.io/r-socialsci/)| (released :tada:) ||
|2023-05-01|[spreadsheets-socialsci](https://datacarpentry.github.io/spreadsheets-socialsci/)|[spreadsheets-socialsci (:mag:)](https://fishtree-attempt.github.io/spreadsheets-socialsci/)|[#48](https://github.com/carpentries/lesson-transition/issues/48)|
|2023-05-01|[sql-socialsci](https://datacarpentry.github.io/sql-socialsci/)|[sql-socialsci (:mag:)](https://fishtree-attempt.github.io/sql-socialsci/)|[#28](https://github.com/carpentries/lesson-transition/issues/28)|

## Library Carpentry


::: {.callout-tip}

### Early transition lessons

Here is a link to tracking issues for lessons whose maintainers have elected to
transition before May: [early transition LibraryCarpentry 
lessons](https://github.com/carpentries/lesson-transition/issues?q=is%3Aopen+is%3Aissue+label%3A%22early+transition%22++librarycarpentry)

:::

```{r}
#| label: lc-table
#| eval: false
#| echo: false
makeit(slist$librarycarpentry)
```

| Expected Transition|Lesson                 |Preview                        | Tracking Issue |
|---------:|:----------------------|:------------------------------|:-------:|
|2023-05-01|[lc-data-intro](https://librarycarpentry.github.io/lc-data-intro/)|[lc-data-intro (:mag:)](https://fishtree-attempt.github.io/lc-data-intro/)|[#60](https://github.com/carpentries/lesson-transition/issues/60)|
|2023-04-24|[lc-data-intro-archives](https://librarycarpentry.github.io/lc-data-intro-archives/)| (released :tada:) |[#61](https://github.com/carpentries/lesson-transition/issues/61)|
|2023-04-20|[lc-git](https://librarycarpentry.github.io/lc-git/)| (released :tada:) |[#63](https://github.com/carpentries/lesson-transition/issues/63)|
|2023-04-25|[lc-marcedit](https://librarycarpentry.github.io/lc-marcedit/)| (released :tada:) |[#64](https://github.com/carpentries/lesson-transition/issues/64)|
|2023-05-01|[lc-open-refine](https://librarycarpentry.github.io/lc-open-refine/)|[lc-open-refine (:mag:)](https://fishtree-attempt.github.io/lc-open-refine/)|[#65](https://github.com/carpentries/lesson-transition/issues/65)|
|2023-05-01|[lc-overview](https://librarycarpentry.github.io/lc-overview/)|[lc-overview (:mag:)](https://fishtree-attempt.github.io/lc-overview/)|[#83](https://github.com/carpentries/lesson-transition/issues/83)|
|2023-05-01|[lc-python-intro](https://librarycarpentry.github.io/lc-python-intro/)|[lc-python-intro (:mag:)](https://fishtree-attempt.github.io/lc-python-intro/)|[#66](https://github.com/carpentries/lesson-transition/issues/66)|
|2023-05-01|[lc-r](https://librarycarpentry.github.io/lc-r/)|[lc-r (:mag:)](https://fishtree-attempt.github.io/lc-r/)|[#19](https://github.com/carpentries/lesson-transition/issues/19)|
|2023-05-01|[lc-shell](https://librarycarpentry.github.io/lc-shell/)|[lc-shell (:mag:)](https://fishtree-attempt.github.io/lc-shell/)|[#67](https://github.com/carpentries/lesson-transition/issues/67)|
|2023-04-21|[lc-spreadsheets](https://librarycarpentry.github.io/lc-spreadsheets/)| (released :tada:) |[#68](https://github.com/carpentries/lesson-transition/issues/68)|
|2023-05-01|[lc-sql](https://librarycarpentry.github.io/lc-sql/)|[lc-sql (:mag:)](https://fishtree-attempt.github.io/lc-sql/)|[#69](https://github.com/carpentries/lesson-transition/issues/69)|
|2023-04-24|[lc-wikidata](https://librarycarpentry.github.io/lc-wikidata/)| (released :tada:) |[#71](https://github.com/carpentries/lesson-transition/issues/71)|

## Software Carpentry

::: {.callout-tip}

### Early transition lessons

Here is a link to tracking issues for lessons whose maintainers have elected to
transition before May: [early transition SoftwareCarpentry 
lessons](https://github.com/carpentries/lesson-transition/issues?q=is%3Aopen+is%3Aissue+label%3A%22early+transition%22++swcarpentry)

:::


```{r}
#| label: swc-table
#| eval: false
#| echo: false
makeit(slist$swcarpentry)
```

| Expected Transition|Lesson                     |Preview                            | Tracking Issue |
|---------:|:--------------------------|:----------------------------------|:-------:|
|2023-05-01|[git-novice](https://swcarpentry.github.io/git-novice/)|[git-novice (:mag:)](https://fishtree-attempt.github.io/git-novice/)|[#72](https://github.com/carpentries/lesson-transition/issues/72)|
|2023-04-27|[git-novice-es](https://swcarpentry.github.io/git-novice-es/)|[git-novice-es (:mag:)](https://fishtree-attempt.github.io/git-novice-es/)|[#73](https://github.com/carpentries/lesson-transition/issues/73)|
|2023-04-24|[make-novice](https://swcarpentry.github.io/make-novice/)| (released :tada:) |[#75](https://github.com/carpentries/lesson-transition/issues/75)|
|2023-04-26|[matlab-novice-inflammation](https://swcarpentry.github.io/matlab-novice-inflammation/)| (released :tada:) |[#76](https://github.com/carpentries/lesson-transition/issues/76)|
|2023-05-01|[python-novice-gapminder](https://swcarpentry.github.io/python-novice-gapminder/)|[python-novice-gapminder (:mag:)](https://fishtree-attempt.github.io/python-novice-gapminder/)|[#77](https://github.com/carpentries/lesson-transition/issues/77)|
|2023-04-20|[python-novice-inflammation](https://swcarpentry.github.io/python-novice-inflammation/)| (released :tada:) |[#22](https://github.com/carpentries/lesson-transition/issues/22)|
|2023-05-01|[r-novice-gapminder](https://swcarpentry.github.io/r-novice-gapminder/)|[r-novice-gapminder (:mag:)](https://fishtree-attempt.github.io/r-novice-gapminder/)|[#78](https://github.com/carpentries/lesson-transition/issues/78)|
|2023-04-27|[r-novice-gapminder-es](https://swcarpentry.github.io/r-novice-gapminder-es/)|[r-novice-gapminder-es (:mag:)](https://fishtree-attempt.github.io/r-novice-gapminder-es/)|[#79](https://github.com/carpentries/lesson-transition/issues/79)|
|2023-05-01|[r-novice-inflammation ](https://swcarpentry.github.io/r-novice-inflammation /)|[r-novice-inflammation  (:mag:)](https://fishtree-attempt.github.io/r-novice-inflammation /)|[#24](https://github.com/carpentries/lesson-transition/issues/24)|
|2023-05-01|[shell-novice](https://swcarpentry.github.io/shell-novice/)|[shell-novice (:mag:)](https://fishtree-attempt.github.io/shell-novice/)|[#80](https://github.com/carpentries/lesson-transition/issues/80)|
|2023-04-24|[shell-novice-es](https://swcarpentry.github.io/shell-novice-es/)| (released :tada:) |[#81](https://github.com/carpentries/lesson-transition/issues/81)|
|2023-05-01|[sql-novice-survey](https://swcarpentry.github.io/sql-novice-survey/)|[sql-novice-survey (:mag:)](https://fishtree-attempt.github.io/sql-novice-survey/)|[#82](https://github.com/carpentries/lesson-transition/issues/82)|

